---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RappPKPLT

<!-- badges: start -->
[![R-CMD-check](https://github.com/soutomas/RappPKPLT/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/soutomas/RappPKPLT/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of RappPKPLT is to provide a Shiny application for interactive simulation using a PK-platelet-GDF15 model in patients with haematological malignancies and solid tumours. 

## Citation

Sou T (2025). _RappPKPLT: Shiny Application for a PK-Platelet-GDF15 Model_. R package version 0.0.0.9000, <https://github.com/soutomas/RappPKPLT>.

```{r}
citation("RappPKPLT") 
```


## Installation

You can install the development version of RappPKPLT from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("soutomas/RappPKPLT")
```

## Example

To run the Shiny application:

```r 
library(RappPKPLT)
app()
```

